---
title: "Lab7"
author: "ZhongShan"
date: "2019/10/22"
output: pdf_document
---



First , let's look at exponential distribution:

P.d.f (Probability density function):

$$f(x) =  \lambda e^{-\lambda x}$$
C.d.f (Cumulative distribution function):

$$F(X) = Pr(x \leq X) =  1- e^{- \lambda X}$$

when $\lambda$ = 1 ( That is when mean = 1):

```{r exponential_pdf ,  fig.width = 4 , fig.height = 4}
lambda = 1

# create a sequence from 0 to 100 with distance 0.01
x = seq(0,20, by= 0.0001)

# create the p.d.f function of exponential for x
f = function(x){lambda*exp(-lambda * x)}
# plot f(x), p.d.f of x
plot(x,f(x),type = "l",col = "blue")

# create the C.d.f function for x
F = function(x){1 - exp(-lambda * x)}
# plot F(x), C.d.f of x
plot(x,F(x),type = "l",col = "blue")

```

Exponential distribution are usually used to model waiting time between independent events. Such as waiting time for passenger entering airport, waiting time to call customer service. Also , some material have an exponential decay. 
 

## simulate 500 exponential distribution

```{r exp_simulate}
lambda = 1

# here we used the rexp function to generate 500 exponential distribution
sample = rexp( n = 500, rate = lambda)

# generate a histgram for the sample ( with 30 seperate bars)
hist(sample, breaks =  30 , col = "red")

# get mean of sample
mean(sample)
# get standard deviation of sample
sd(sample)

```


## if we generate n = 2 exponential distribution each time, and look at the distribution of the mean 

```{r mean_simulate}
lambda = 1

# define sample to be a vector
sample = c()

# a for loop, repeat 500 times
for(i in 1:500){
  # generate 2 exponential distribution
  a = rexp( n = 2, rate = lambda)
  # take the average of them
  b = mean(a)
  # save our sample mean ( append value of b to our sample)
  sample = c(sample , b)
}

# generate a histgram for the sample ( with 30 seperate bars)
hist(sample, breaks =  30 , col = "red")

# get mean of sample
mean(sample)
# get standard deviation of sample
sd(sample)

```

# First, try get the average n = 30 on your own, finish table 7.1

# Second, try uniform and finish table 7.2

use runif(n=500,min = 0 , max = 1) to generate 500 uniform distribution with a = 0 and b = 1 

# Third, try normal and finish table 7.2

use rnorm(n=500,mean = 0 , sd = 1) to generate 500 standard normal distribution with mean = 0 and standard deviation = 1 

# Finish all discussion questions


